Holomorphic field theories and higher algebra

### 2022-08-19 draft.tex
adding polydiscs section

@@

>>>>

\brian{complex geometry, dolbeault, dg stuff.}

@@

\section{Algebraic structures parametrized by configuration spaces}

Associative algebras arise in quantum mechanics, we have argued, because the spacetime of a mechanical system is a line (``time'').
If we organize the observables (or operators) by when they happen in time,
it corresponds to writing them left-to-right as products in an algebra.
A natural question to ask then is what kind of higher algebraic structure captures how observables behave for theories in higher dimensions?
The shortest answer is ``factorization algebras,'' and we will describe and explore this notion in Section~\ref{sec fact alg},
but there are nice answers for two special classes of theories that we will develop now:
\begin{itemize}
\item For a topological field theory on $\RR^d$ (which we'll define in a moment),
the observables form an algebra over the {\em little $d$-disks operad}~$\Disc_d$ (sometimes also known as the $E_d$ operad). 
Equivalently, one says the observables are an $E_d$-algebra. 
This notion was introduced by algebraic topologists in the 1960s, 
so there is a rich body of work to draw upon.
\item For a holomorphic field theory on $\CC^d$,
the observables form an algebra over the $d$-polydiscs operad~$\PDisc_d$.
This notion was introduced only recently in~\cite{CG1}.
\end{itemize}
We will make the assertions above precise (in part by adding some natural but necessary hypotheses on a theory)
and develop them in parallel.
As a particularly illuminating example, we will explore the $d=1$ case rather closely and explain in what sense a vertex algebra is a kind of ``holomorphic associative algebra.''
We will also discuss the polydiscs algebras for which the higher Kac-Moody algebras are a Lie-algebraic shadow.

Before jumping into the main story, we mention a motivation for talking about $E_d$- and $\PDisc_d$-algebras in parallel.
By dealing with both, we are suggesting, of course, that there is a natural analogy and hence a useful transfer of intuition between the settings of topological and holomorphic field theories.
But there is a stronger, technical relationship that we'll develop via a version of dimensional reduction.
From each holomorphic field theory in complex dimension $d$, 
we'll extract an $E_d$-algebra.
This construction generalizes the relationship between the Kac-Moody vertex algebra of a Lie algebra $\fg$ at level $k$ and the central extension of the loop algebra~$L\fg$.
We expect this correspondence to bear rich fruit.
\owen{that metaphor's a bit fruity}

\subsection{Generalizing associative algebras for topological field theories}

We want to describe the algebraic structures that appear in $d$-dimensional topological field theories,
as a model for holomorphic field theories.
It will be helpful to use the language of operads, which are an efficient and powerful tool for defining and studying algebraic structures,
so we will gloss the key ideas of operads briefly and then turn to describing the operads relevant to TFTs.
A more extensive discussion can be found in \cite{CG1}, with \cite{ES} studying the topological setting in an elegant way.

An associative algebra is, by definition, a vector space $A$ with a linear map $\mu: A\otimes A \to A$ satisfying that the linear map $\mu \circ (\id \otimes \mu): A^{\otimes 3} \to A$ equals the linear map $\mu \circ (\mu \otimes \id)$.
(Let's ignore the other data and conditions for the moment.)
Nearly all flavors of algebras --- Lie, Poisson, and so on --- have a similar definition:
one has a collection of multilinear maps that satisfy some relations.
An operad is a way of specifying such data, so there is an associative operad $Ass$,
a Lie operad $Lie$, and so on.

Before sketching the definition, we give a concrete example.
Let $V$ be a vector space.
Then every $n$-fold multilinear operator on $V$ is an element of $\Hom(V^{\otimes n}, V)$;
that vector space parametrizes all possible $n$-ary operations on $V$.
One can also compose such operations to produce new ones.
For instance, given $\mu : V^{\otimes m} \to V$ and $\nu: V^{\otimes m} \to V$, we can put the output of $\mu$ into the $i$th input of $\nu$ to produce a new operation
\[
\begin{array}{cccc}
\nu \circ_i \mu: & V^{\otimes m+n-1} & \to & V\\
& v_1 \otimes \cdots \otimes v_{m+n-1} & \mapsto & \nu(v_1 \otimes \cdots \otimes \mu(v_i, \ldots, v_m), v_{m+1}, \ldots, v_{m+n-1})
\end{array}
\]
\owen{finish the formula! make it agree with conventional formulas}
where $i$ can run over any index between 1 and $n$.
We call this collection of data the {\em endomorphism operad of $V$}, denote $\End_V$.
It consists of 
\begin{itemize}
\item a list of vector spaces labelling $n$-ary operations, with 
\[
\End_V(n)= \Hom(V^{\otimes n}, V),
\]
with $n \in \NN$, and
\item a list of linear maps
\[
\circ_i : \End_V(n) \otimes \End_V(m) \to \End_V(n+m-1)
\]
for every pair $n$ and $m$ and where $1 \leq i \leq n$.
\end{itemize}
There are certain natural relations when one does multiple compositions, like $\mu \circ_i (\nu \circ_j \pi)$, arising from how multilinear maps compose.

Just as the model case of an associative algebra is $\End(V) = \Hom(V,V)$ (the ring of square matrices),
the endomorphism operad is the model case of operads.
A linear operad $P$ consists of a list of vectors $\left(P(n) \right)_{n \in \NN}$, where each $P(n)$ is a vector space describing $n$-ary operations, and a list of linear maps $\left(\circ_i\right)$.
We will not describe the relations, but resemble those of an endomorphism operad.

\begin{rmk}
The reader might ask why the adjective {\em linear} was appended before {\em operad}.
The reason is that we discussed algebraic operations on vector spaces,
but one can, of course, discuss analogs in other settings.
For instance, a monoid is a set $M$ with a multiplication map satisfying an associativity constraint.
One can talk about operads in sets (``an operad in sets $P$ has a set $P(n)$ of $n$-ary operations for every $n \in \NN$ \dots'') or in topological spaces or in dg vector spaces.
In fact, the theory works in any symmetric monoidal category. 
For the most part, we will work with vector spaces below.
\end{rmk}

Let us now raise another useful analogy.
To define a module for an associative algebra $A$, one specifies an algebra map $\rho: A \to \End(V)$.
This map encodes how $A$ acts on $V$.
Similarly, to give an algebra for an operad $P$, one specifies an operad map $\rho: P \to \End_V$.
This map picks out specific multilinear operations on $V$ that will satisfy the relations we want.
For instance, if $Pois$ is the Poisson operad, then $Pois(2) \cong \CC^2$ and this vector space is spanned by an element $\cdot$, the commutative product, and $\{\}$, the Poisson bracket.
Given a $P$-algebra $V$, the map $\rho(2): Pois(2) \to \End_V(2)$ thus tells us both the commutative and Poisson bracket put upon~$V$.
(The reader might enjoy trying to work out $Pois(3)$ and how to get elements there by composing binary operations.)
Alternatively, by applying the hom-tensor adjunction to $\rho(2)$, we have a map
\[
Pois(2) \otimes V^{\otimes 2} \to V
\]
that evaluates a binary operation with a pair of inputs.

By working at the level of operads, one can obtain universal results that hold for all algebras over a given operad.
For example, there is an operad map $b: Lie \to Pois$ that, at the level of the binary operations, includes the bracket, 
and this map induces the functor $b^*: \Alg_{Pois} \to \Alg_{Lie}$ where a Poisson algebra is ``forgotten'' to a Lie algebra.

So far we have only discussed putting algebraic structures on a single vector space $V$,
but it is possible to allow collections of vector spaces.
For instance, the pair of an algebra and a module provides an example of ``two-colored operad'' as the collection always consists of two vector spaces.
When one allows multiple objects, one works with {\em colored operads} or, as an alternative terminology, {\em multicategories}.

\begin{rmk}
For motivational introductions, we recommend \cite{StashAMS} and \cite{Val12}.
For systematic development of the theory, one might start with \cite{LodVal}, \owen{others}
Operads now have an extensive literature, and there is a body of deep results (such as Koszul duality) with far-reaching consequences throughout mathematics.
\end{rmk}

With this language to hand, we now turn to generalizing associative algebras for the setting of topological field theories. 
Our goal is to formulate a colored operad that captures the behavior of the observables of a topological field theory.

The heuristic idea is straightforward.
Given a field theory $\cT$ on $\RR^d$, there is a vector space (or possibly dg vector space) $\Obs_\cT(D_r(x))$ of measurements one can make in the open disk $D_r(x)$ of radius $r$ around the point $x$.
Any measurement in a small disk should provide a measurement on a bigger disk,
so there is a map $\Obs_\cT(D_r(x)) \to \Obs_\cT(D_R(y))$ whenever $D_r(x) \subset D_R(y)$.
Thus we have a collection of vector spaces labeled by the disks in $\RR^d$,
and we have identified a class of unary operations determined by inclusion.

There should also be natural $n$-ary operations encoding how to combine observables from several distinct disks to give an observable on a big disk.
Start with $n$ disks $D_{r_1}(x_1)$, \dots , $D_{r_n}(x_n)$ whose closures are pairwise disjoint, and let $D_R(y)$ be a big disk containing all the smaller disks.
Then we want a map
\[
\Obs_\cT(D_{r_1}(x_1)) \otimes \cdots \otimes \Obs_\cT(D_{r_n}(x_n)) \to \Obs_\cT(D_R(y)).
\]
In the limit when the big disk is all of $\RR^d$ (i.e., $R = \infty$) and the input radii $r_i$ are very small, 
this map should encode the $n$-point functions beloved of physicists.

So far we have described a structure that observables should have for any field theory on~$\RR^d$.
For a topological field theory, we expect that the size of a disk does not matter:
for any inclusion $D_r(x) \subset D_R(y)$, the map $\Obs_\cT(D_r(x)) \to \Obs_\cT(D_R(y))$ is an equivalence.
This condition implies that we can always shrink the input radius as small as we want and we can always take the output radius to be a fixed value, say $R =1$.
In other words, the unary operations are parametrized by a point in the unit disk;
we have a local system of isomorphisms.

For $n$-ary operations we can likewise shrink the input radii as small as we want.
Thus the $n$-ary operations should be parametrized by the configuration space of $n$ points inside the unit disk.
(Rather, we can recover all $n$-ary operations knowing this information.)
We expect that these $n$-ary operations should also define a local system.

Our list of expectations is motivated by the examples of topological field theories that physicists typically give, rather than the Atiyah-Segal approach in terms of functors out of bordism categories.
Loosely speaking, a classical field theory (defined by a Lagrangian density, also known as an action functional) is ``topological'' if solutions to the equations of motion do not depend on the geometry of the spacetime manifold but only on its smooth structure (or other differential-topological features, like orientations).
A model example is Chern-Simons theory on oriented 3-manifolds for compact Lie group~$G$:
the space of solutions to the equations of motion on $M$ is the moduli space of flat $G$-bundles on $M$.
The observables for a classical field theory on $M$ means the commutative algebra of functions on solutions to the equations of motion on $M$.
In particular, for $M$ a disk, the size of the disk will not affect the algebra of observables,
and inclusions of disks leads to isomorphisms of observables.
Several of these features extend to the quantum field theories that arise by quantizing such topological classical theories;
the observables continue to form a vector space but are not commutative algebras anymore.
(See \cite{CG1, CG2} for a precise mathematical formulation of this idea, which is a natural extension of deformation quantization to higher dimensions.)

\begin{rmk}
There are examples of TFTs from physics where the solutions do not satisfy this condition,
such as the $A$-model of mirror symmetry.
In such cases, however, the observables are typically the de Rham complex (or some other model for cohomology) of the space of solutions,
and these observables do satisfy the conditions we've specified.
\end{rmk}

We are now in a position to offer a nice operad that should describe the observables of a topological field theory.
This operad was introduced by algebraic topologists for wholly distinct purposes (understanding $d$-fold based loop spaces),
so a remarkable dialogue has opened between topologists and physicists.
We will start, following the topologists, in the category $Top$ of topological spaces
where we use the cartesian product for the symmetric monoidal structure.
An operad in this category will be called a {\em topological operad}.

\begin{dfn}
The {\em little $d$-disks operad} $\Disc_d$ is the topological operad whose space of $n$-ary operations is
\begin{align*}
\Disc_d(n) = \{ (x_1, \ldots, x_n; r_1, &\ldots, r_n)  \in D_1(0)^n \times (0,1)^n \;|\; \\
&\text{the closure of the disks $\overline{D_{r_i}(x_i)}$ is pairwise disjoint}\}.
\end{align*}
The composition $\mu \circ_i \nu$ is given by rescaling the unit disk that labels the output of $\nu$ to $r_i$ and then embedding it into the disk~$D_{r_i}(x_i)$.
\end{dfn}

\owen{Draw some 2d pictures and unpack a little. Mention pair of pants \& OPE} 
In this sense, it captures the dependence on the disks.

Observables, however, are supposed to live in vector spaces or dg vector spaces,
so we need to explain how to get algebras in that setting.
Thankfully, it is straightforward to get a linear version of this operad a dg operad (i.e., operad with values in dg vector spaces and using the tensor product as the symmetric monoidal product).
One simply takes the singular chain complex on each space of operations:
for each natural number $n$, take $C_*(\Disc_d(n); \CC)$ and take the induced chain map 
\[
C_*(\circ_i): C_*(\Disc_d(n); \CC) \otimes C_*(\Disc_d(m); \CC) \to C_*(\Disc_d(n+m-1); \CC)
\]
to produce a dg operad we denote~$C_*(\Disc_d)$.
(Note that as we always want to work with cochain complexes, we regrade the usual singular chains $C_*(X, \CC)$ to sit in nonpositive cohomological degrees. 
Likewise the composition $C_*(\circ_i)$ is then a cochain map.)

\begin{dfn}
An {\em algebra over the little $d$-disks operad} (or little $d$-disks algebra or $E_d$-algebra) is a cochain complex $A$ that is an algebra over the dg operad~$C_*(\Disc_d)$.
\end{dfn}

We can state now encapsulate our expectations from above:
\begin{quote}
the observables of a topological field theory on $\RR^d$ are a little $d$-disks algebra.
\end{quote}
There is a setting where a precise version of this statement was proven, by Elliott and Safronov, for a mathematically well-defined class of Lagrangian field theories.

\owen{give a nice version of their statement, with this as a first attempt}

\begin{thm}[\cite{EllSaf},\owen{precise location}]
Let $\cT$ be a classical field theory on $\RR^d$ in the sense of~\cite{CosBook},
and let its observables be constructed following~\cite{CG2}.
If the theory satisfies 
\begin{enumerate}
\item[(i)] $\cT$ is equivariant under the action of the translation group,
\item[(ii)] the action of the translation Lie algebra is homotopically trivialized, and
\item[(iii)] the extension of observables along an inclusion of disks is a quasi-isomorphism,
\end{enumerate}
then the observables form a little $d$-disks algebra.
\end{thm}

The notion from \cite{CosBook} articulates Lagrangian field theories whose linearized equations of motion are elliptic in nature;
it uses (and mathematically articulates) the Batalin-Vilkovisky formalism,
which is inherently homological.
In particular, there is an underlying graded vector space of ``fields,''
and the observables are a dg commutative algebra given a symmetric algebra on the linear dual to the fields and equipped with a differential $d_\cT$ that is determined by the Lagrangian density of the theory.
Item (ii) above then means that each vector field $\partial_i$ acts by a degree 0 cochain map $D_i$ on the observables and there is a degree one cochain homotopy $\eta_i$ on the observables such that $[d_\cT, \eta_i]~=~D_i$.

This theorem applies to many well-known examples from physics, such as 
\begin{itemize}
\item the topological $B$-model of maps from an oriented surface into a Calabi-Yau manifold (constructed by Li and Li \cite{LiLi} in a setting where \cite{EllSaf} applies);
\item Chern-Simons gauge theory of flat $G$-bundles on an oriented 3-manifold (constructed, essentially, by Axelrod-Singer \cite{AxeSin} and Kontsevich \cite{KonECM} but articulated in this setting by Costello \cite{CosBook});
\item Rozansky-Witten theory of maps from an oriented 3-manifold into a complex manifold \cite{ChanLeungLi}; and
\item the Kapustin-Witten gauge theory for oriented 4-manifolds \cite{EGW},
\end{itemize}
among other examples of topological AKSZ theories, such as BF theories.

For physicists, we note that the proof uses a version of Witten descent.
Indeed, descent can be used to produce interesting operations in these disk algebras,
so that many familiar constructions from the physical approach to TFTs fit cleanly and easily into this framework.

\owen{Stuff about formality? functorial field theories?}

\subsection{Generalizing algebras for holomorphic field theories}

We now turn to the problem of describing observables of a holomorphic field theory on~$\CC^d$,
and we follow an approach similar to the topological case just discussed.

In the setting of a holomorphic field theory, we expect the observables to have a nontrivial dependence on the radius of a disk.
Consider, for example, that 
when $D_r(x) \subset D_R(y) \subset \CC$ are open disks in the plane,
the restriction map of holomorphic functions
\[
\cO(D_R(y))\to \cO(D_r(x))
\]
is not an isomorphism,
and the sheaf $\cO$ provides a fundamental model for how the solutions of the equations of motion should behave for a holomorphic field theory.
We will assume, however, that a holomorphic theory is equivariant under translations of $\CC^d$ and that the observables in a disk $D_r(X)$ are equivalent to the observables in a translate~$D_r(x+z)$.
Thus, we will have a colored operad whose colors are labeled by radii~$r \in (0,\infty)$,
as we merely have to specify the observables on a disk~$D_r(0)$.

We now introduce a small tweak.
Instead of working with disks, we work with polydisks: for $w = (w_1, \ldots, w_d) \in \CC^d$, the polydisk of radius $r$ around $w$~is
\[
PD_r(w) = \{ z \in \CC^d \;|\; |z_i - w_i| < r \text{ for all $i$}\}.
\]
We work with polydisks because it is easier to describe holomorphic functions on a polydisk than on a disk;
one can borrow results from single-variable complex analysis.
With this notion in hand, we introduce our main character.

\begin{dfn}
The {$d$-polydisks operad} $\PDisc_d$ is the colored operad in the category of complex manifolds where each positive real number $r \in (0,\infty)$ is a color 
and where there is a complex manifold of $n$-ary operations
\begin{align*}
\PDisc_d(r_1, \ldots, r_n| R) = \{ (w_1, \ldots,& w_n) \in PD_R(0)^n \;|\; 
\text{the closure of the polydisks $\overline{PD_{r_i}(w_i)}$}\\ 
&\text{ is pairwise disjoint and each is contained in $PD_R(0)$}\}
\end{align*}
for any list of radii $r_1,\ldots, r_n, R$.
This manifold is always an open subset of~$PD_R(0)^n$. 
(Note that the manifold is empty for many values.)
There is a composition
\[
\circ_i: \PDisc_d(r_1, \ldots, r_n| R) \times \PDisc_d(s_1, \ldots, s_m| S) \to \PDisc_d(r_1, \ldots, s_1, \ldots, s_m, r_{i+1}, \ldots, r_n| R)
\]
only when $r_i = S$, 
and in that case, the composition $\mu \circ_i \nu$ is given by embedding an output polydisk into an input polydisk of the same radius.
(Composition is not defined if the radii do not match.)
\end{dfn}

We are again thinking about configuration spaces --- here of polydisks inside larger polydisks --- but we are remembering the complex structure explicitly.
To describe observables, we want to produce a dg colored operad that encodes the holomorphic nature of this situation.
We do {\em not} want to take singular chains, which would only remember the homotopy type;
instead, we choose to take the Dolbeault complex of each configuration space.
Note, however, that taking the Dolbeault complex is a contravariant functor,
so we get a {\em co}\/operad rather than an operad.
This notion bears the same relationship to operad as a coalgebra does to an algebra;
one simply reverses all the arrows and asks for an appropriate variant of the relations.
For instance, there is a composition
\begin{align}
\label{pdcirc}
\circ_i: \Omega^{0,*}(\PDisc_d(r_1, \ldots, s_1, &\ldots, s_m, r_{i+1}, \ldots, r_n| R)) \to \\
&\Omega^{0,*}(\PDisc_d(r_1, \ldots, r_n| R)) \otimes \Omega^{0,*}(\PDisc_d(s_1, \ldots, s_m| S))
\end{align}
\owen{I don't know how to eliminate the two numbers}
when $r_i = S$, and in that case, the composition $\mu \circ_i \nu$ is given by embedding an output polydisk into an input polydisk of the same radius.
(Composition is not defined if the radii do not match.)

An important technical point arises here: 
we need to be careful about functional analysis.
The wedge product map
\[
\Omega^{0,*}(X) \otimes \Omega^{0,*}(Y) \to \Omega^{0,*}(X \times Y)
\]
is not a quasi-isomorphism in general (unlike with de Rham complexes),
but the completed projective tensor product as topological vector spaces 
\[
\Omega^{0,*}(X) \widehat{\otimes}_\pi \Omega^{0,*}(Y) \to \Omega^{0,*}(X \times Y)
\]
is an isomorphism.
(We use here the standard Fr\'echet topology on smooth functions, extended to sections of vector bundles.)
Hence we should work in some category of cochain complexes of well-behaved topological vector spaces, such as convenient vector spaces, or something related.
This requirement makes sense when geometry matters (e.g., using the Dolbeault complex) and not just topology.
For an extensive discussion of these issues, see the appendices of~\cite{CG1}.
From hereon we will ignore function-analytic aspects and write $\otimes$,
with an appropriate symmetric monoidal category left implicit.

\begin{dfn}
The {\em $d$-polydisks dg cooperad} is the colored operad in the category of dg vector spaces where each positive real number $r \in (0,\infty)$ is a color 
and where there is a dg vector space of $n$-ary cooperations
\[
\Omega^{0,*}(\PDisc_d(r_1, \ldots, r_n| R)) 
\]
for any list of radii $r_1,\ldots, r_n, R$.
There is a composition
\[
\circ_i: \Omega^{0,*}(\PDisc_d(r_1, \ldots, s_1, \ldots, s_m, r_{i+1}, \ldots, r_n| R))\to \Omega^{0,*}(\PDisc_d(r_1, \ldots, r_n| R)) \otimes \Omega^{0,*}(\PDisc_d(s_1, \ldots, s_m| S))
\]
only when $r_i = S$, 
and in that case, the composition $\mu \circ_i \nu$ is given by embedding an output polydisk into an input polydisk of the same radius.
(Composition is not defined if the radii do not match.)
\end{dfn}

An algebra $A$ over this cooperad means that for each radius~$r$, 
there is a dg vector space $A(r)$, and for any list of radii $r_1,\ldots, r_n, R$,
there is a cochain map
\[
\alpha(r_1, \ldots, r_n| R): A(r_1) \otimes \cdots \otimes A(r_n) \to A(R) \otimes \Omega^{0,*}(\PDisc_d(r_1, \ldots, r_n| R)) .
\]
To invest the map $\alpha$ with more meaning, 
pick a real, closed submanifold $T \subset \PDisc_d(r_1, \ldots, r_n| R)$, along which one can integrate $(0,k)$-forms.
For instance, for any inputs $a_i \in A(r_i)$ and any cocycle $\omega \in \Omega^{0,k}(\PDisc_d(r_1, \ldots, r_n| R))$, we get an element in $A(R)$~by
\[
\int_T \alpha(a_1 \otimes \cdot \otimes a_n) \wedge \omega,
\]
where we have suppressed distracting notation from~$\alpha$.

We will now examine the case $d=1$ in some detail and relate such algebras to vertex algebras.
Afterward, we explain how holomorphic field theories produce such algebras,
by a result analogous to Elliott and Safronov's.
In particular, a holomorphic version of Witten descent gives a useful method for producing interesting observables for holomorphic field theories.

\subsubsection{Vertex algebras from the $d=1$ case}

In the case $d=1$, it is possible to relate polydisks algebras to vertex algebras.
More precisely, when the polydisk algebra has a nice action of the rotation group~$U(1)$,
one can extract a vertex algebra: 
see Chapter 5 of~\cite{CG1} for a detailed treatment and examples like the free $\beta\gamma$ system and the Kac-Moody vertex algebras.
Here we will analyze the cohomology of the cooperad and what kind of information it encodes, with a view towards motivating the relationship to vertex algebras.

It is easiest to work with extremal values of the radii.
We take the output radius to be $R = \infty$,
so that the outputs are observables on all of~$\CC$.
We take the input radii to be $r_i = 0$,
so that the inputs are observables supported at the points $w_i$.
(A physicist might call these ``local operators.'')
This input value is not allowed in the definition, but it arises as a natural limit.
In any case, it is natural to think about the complex manifold ${\rm Conf}_n(\CC)$ of configurations of $n$ distinct points in~$\CC$:
it is
\[
{\rm Conf}_n(\CC) = \CC^n \setminus \{\text{union of the diagonals $\{ w_i = w_j\}$}\}.
\]
Note that for any finite and nonzero values of radii, there is an inclusion
\[
\PDisc_d(r_1, \ldots, r_n| R) \hookrightarrow {\rm Conf}_n(\CC).
\]
We now turn to examining the Dolbeault cohomology.

It is easy to see
\[
{\rm Conf}_n(\CC) \cong \CC \times (\CC^\times)^{n-1}
\]
by sending a configuration $(w_1,\ldots, w_n)$ to $(w_1, w_2 - w_1, \ldots, w_n-w_{n-1})$.
(We could replace $w_1$ by any $w_j$, or even the sum of them all.)
Hence, the Dolbeault cohomology consists of holomorphic functions on this space;
there is no higher cohomology.
Inside the holomorphic functions, as a dense but understandable subalgebra, are the algebraic functions:
\[
\CC[w_1, (w_1 - w_2)^{\pm 1}, \ldots, (w_n - w_{n-1})^{\pm 1}] \subset H^{0,*}({\rm Conf}_n(\CC)).
\]
Here $(w_j - w_{j-1})^{\pm 1}$ means that the function $1/(w_j - w_{j-1})$ is also a generator.
Each such algebraic function provides an operation on $H^*(A)$, where $A$ denotes a polydisk algebra.

Let us unravel things in the special case of two points.
For simplicity, we will fix $w_1 = 0$ so that we focus on where place the other point $w_2 \in \CC^\times$.
We will use $z$ to denote this point $w_2$.
Then the binary co-operations are parametrized by $\CC[z, z^{-1}]$.
Let 
\[
V = \lim_{r \to 0} H^*(A(D_r(0)))
\]
denote the cohomological observables ``supported at the origin.''
(It would be better to take the homotopy limit of the $A(D_r(0))$,
but we leave the experienced reader to make such adjustments.)
For any two elements $a, b \in V$,
we then have an element
\[
a
\]

\subsubsection{Polydisks algebras from holomorphic field theories}

Let 
\[
\ft_\CC = \CC \otimes_\RR \ft = \text{span}_{\CC}\{\partial/\partial z_1, \ldots, \partial/\partial z_d, \partial/\partial \zbar_1, \ldots, \partial/\partial \zbar_d  \}
\]
denote the complexification of the Lie algebra~$\ft$ of translations.
Let $\ft_{\zbar}$ denote the subalgebra spanned by all the~$\partial/\partial \zbar_i$.

\begin{thm}[\cite{CG1},\owen{precise location}]
Let $\cT$ be a classical field theory on $\CC^d$ in the sense of~\cite{CosBook},
and let its observables be constructed following~\cite{CG2}.
If the theory satisfies 
\begin{enumerate}
\item[(i)] $\cT$ is equivariant under the action of the translation group and
\item[(ii)] the action of the Lie algebra $\ft_{\zbar}$ is homotopically trivialized,
\end{enumerate}
then the observables form a $d$-polydisks algebra.
\end{thm}

This result is analogous to Elliott and Safronov's, although it predated (and inspired) it.
It applies to the theories that are the focus of this survey.
One can mimic the version of Witten descent for the topological case to produce observables from local observables.

\subsubsection{From topological to holomorphic}

We remark on a simple consequence of this toolkit that may nonetheless be useful:
one can view a topological field theory on $\RR^{2d}$ as a special kind of holomorphic field theory on~$\CC^{d}$.
This situation has been exploited to good effect in the $d=1$ case,
where people sometimes present an $E_2$-algebra as a dg vertex algebra with extra data and special properties \owen{citations? discussion of applications?}.

The essential idea is simple.
On a complex manifold $X$, there is a cochain map
\[
\Omega^*(X) \to \Omega^{0,*}(X)
\]
where one quotients by the dg ideal of Dolbeault $(p,q)$-forms where $p \geq 1$.
If we consider the complex manifold $\PDisc_d(r_1,\ldots,r_n|R)$, 
we get a map from its de Rham complex --- which only cares about the topology of that configuration space --- to its Dolbeault complex --- which is sensitive to its complex geometry.
Hence an algebra over the cooperad $\Omega^*(\PDisc_d)$ forgets to an algebra over the cooperad~$\Omega^{0,*}(\PDisc_d)$.
Moreover, it is straightforward (if one is comfortable with operads and higher categories) to show that 
\begin{enumerate}
\item algebras over the dg operad $C_*(\PDisc_d)$ are equivalent to algebras over the dg cooperad~$\Omega^*(\PDisc_d)$, as $\infty$-categories, and
\item $E_{2d}$-algebras are equivalent to the algebras over $C_*(\PDisc_d)$ such that an inclusion of a polydisk is always a quasi-isomorphism (the ``locally constant'' algebras).
\end{enumerate}
The second item holds because any configuration space of polydisks is weakly equivalent, as a topological space, to the analogous configuration space of disks.
Thus we have sketched the following result.

\begin{thm}
The observables of a topological field theory on $\RR^{2d}$ determine an algebra over the polydisks cooperad~$\Omega^{0,*}(\PDisc_d)$.
\end{thm}

In Section~\ref{???} we will examine another relationship --- generalizing the compactification/chiralization on $\CC$ --- that yields an $E_d$ algebra from a $\PDisc_d$-algebra.
